The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-12-12 manuscript.Rmd
[fix #74] include proportion of samples collected on shelf

n_spp_west <- combined_records %>%
    dplyr::filter(is_west_coast == TRUE) %>%
    count_spp
```

Most samples have been collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A). More records have been collected from the Atlantic Ocean, than the Gulf of Mexico, and the Pacific Ocean (`r format(sum(combined_records$is_east_coast), big.mark=",")`, `r format(sum(combined_records$is_in_gom), big.mark=",")`, and `r format(sum(combined_records$is_west_coast), big.mark=",")` records respectively). The highest species richness has been recorded from the Gulf of Mexico (`r format(n_spp_gom, big.mark=",")` species), followed by the Atlantic Ocean (`r format(n_spp_east, big.mark=",")` species), and the Pacific Ocean (`r format(n_spp_west, big.mark=",")` species).

>>>>

n_spp_west <- combined_records %>%
    dplyr::filter(is_west_coast == TRUE) %>%
    count_spp

prop_idigbio_continental_shelf <-
   mean(idigbio_us_inverts_records_all_with_depth$marmap_depth < 0 &
        idigbio_us_inverts_records_all_with_depth$marmap_depth > -200) * 100 %>%
   format_output()

prop_obis_continental_shelf <-
    mean(obis_us_inverts_records_all_with_depth$marmap_depth < 0 &
         obis_us_inverts_records_all_with_depth$marmap_depth > -200) * 100 %>%
    format_output()
```

Most samples have been collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A), with `r prop_idigbio_continental_shelf`% (iDigBio) and `r prop_obis_continental shelf`% (OBIS) of the records collected between 0-200m. More records have been collected from the Atlantic Ocean, than the Gulf of Mexico, and the Pacific Ocean (`r format(sum(combined_records$is_east_coast), big.mark=",")`, `r format(sum(combined_records$is_in_gom), big.mark=",")`, and `r format(sum(combined_records$is_west_coast), big.mark=",")` records respectively). The highest species richness has been recorded from the Gulf of Mexico (`r format(n_spp_gom, big.mark=",")` species), followed by the Atlantic Ocean (`r format(n_spp_east, big.mark=",")` species), and the Pacific Ocean (`r format(n_spp_west, big.mark=",")` species).
